---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 10,
  fig.retina = 3
)
```

# ggsegJHU

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegJHU/workflows/R-CMD-check/badge.svg)](https://github.com/ggsegverse/ggsegJHU/actions)
<!-- badges: end -->

This package provides JHU and ICBM white matter atlases formatted for
use with [ggseg](https://ggseg.github.io/ggseg/) and
[ggseg3d](https://ggseg.github.io/ggseg3d/).

| Atlas | Function | Regions | Reference |
|-------|----------|---------|-----------|
| JHU Tracts | `jhu_tracts()` | 20 | Hua et al. (2008) |
| JHU ICBM-DTI-81 Labels | `jhu_labels()` | 48 | Mori et al. (2005) |
| ICBM DTI-81 | `icbm()` | 26 | Mori et al. (2005) |

To learn how to use these atlases, please look at the documentation for
[ggseg](https://ggseg.github.io/ggseg/) and
[ggseg3d](https://ggseg.github.io/ggseg3d/).

## Installation

You can install ggsegJHU from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("ggsegverse/ggsegJHU")
```

## Atlases

```{r}
#| label: jhu-tracts
library(ggseg3d)
library(ggsegJHU)

ggseg3d(atlas = jhu_tracts())
```

```{r}
#| label: jhu-labels
ggseg3d(atlas = jhu_labels())
```

```{r}
#| label: icbm
ggseg3d(atlas = icbm())
```
